---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lm2Wsmry)
```

##### For non-NA case
A data set containing information regarding violent crime rates by us state named "USArrests" is used to test for non-NA case in this package.
```{r}
data("USArrests")
```

##### For NA-included case
A data set containing information regarding air quality named "airquality" is used to test for NA-included case in this package.
```{r}
data("airquality")
```


### To use the function `lm2`:
lm2 is a function that is designed to fit linear model regressions. There are three input argumanet, which are \textbf{\textit{formula}}, \textbf{\textit{data}} and \textbf{\textit{res_display}}. \textbf{\textit{formula}} is the formula that linear regressions follow, \textbf{\textit{data}} is the data set that regression depend on, and \textbf{\textit{res_display}} is used to control whether the function display the result or not. The input value for \textbf{\textit{formula}} and \textbf{\textit{data}}are required, but that for \textbf{\textit{res_display}} is not required. 
    
**Use the function lm2 to display result**         
*Note: the default of res_display is set to TRUE if input value is excluded*
```{r, message=FALSE}
lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests)
```

**Use the function lm2 to return output without result displaying**
```{r}
# nothing shows up
lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests, res_display = F)
```

```{r}
# get the information in the output
result = lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests, res_display = F)
result$coefficients
```

**Include interaction terms** 
Like the `lm()`, there are two ways to include interaction terms:

1) Using \textbf{*} to include main effects and interaction 
```{r}
lm2(formula = Rape ~ Murder*Assault, data = USArrests)
```
  
2) Using \textbf{:} to include \textb{only} the interaction and exclude main effects
```{r}
lm2(formula = Rape ~ Murder:Assault, data = USArrests)
```

**Deal with NA valus** 

1) Using 'na.omit' or without any action for \textbf{'na.handle'}  
```{r}
lm2(formula = Temp ~ Wind + Solar.R, data = airquality, na.handle = "na.omit")
```

2) Using 'na.fail' for \textbf{'na.handle'}  
```{r, error=TRUE}
lm2(formula = Temp ~ Wind + Solar.R, data = airquality, na.handle = "na.fail")
```


### Benchmark `lm2` against `lm`:
In this section, we will compare the outputs of `lm2()` against `lm()`. To begin, we will save the outputs from both `lm2` and `lm` functions.
```{r}
mod_lm2 <- lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests, res_display = F)
mod_lm <- lm(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests)
```
      
Below, we use `all.equal` and `mark` functions from base R and `bench` package, respectively, to compare outputs from `lm2` and `lm`.
  
**Compare: Coefficients **
```{r}
# Note default na.action matches lm function
all.equal(mod_lm2$coefficients, mod_lm$coefficients) 
bench::mark(mod_lm2$coefficients, mod_lm$coefficients) 
```

**Compare: Fitted Values**
```{r}
all.equal(mod_lm2$fitted.values, mod_lm$fitted.values) 
bench::mark(mod_lm2$fitted.values, mod_lm$fitted.values) 
```

### To use the function `summarylm2()`:
`summary_lm2` is a function that takes an output of function `lm2()` and returns important statistics information for a linear regression model. There are two input argumanet, which are \textbf{\textit{lm_mod}} and \textbf{\textit{res_display}}. \textbf{\textit{lm_mod}} is the result given by `lm()`, and \textbf{\textit{res_display}} is used to control whether the function display the result or not. The input value for \textbf{\textit{lm_mod}}are required, but that for \textbf{\textit{res_display}} is not required. 

**Use the function summary_lm2 to display result**
*Note: the default of res_display is set to TRUE if input value is excluded*
```{r}
summary_lm2(lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests, res_display = F))
```
  
**Use the function lm2 to return output without result displaying**
```{r}
# nothing shows up
summary_lm2(lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests, res_display = F), res_display = F)
```

#### Access calculated statistics
To save important information that calculated, `$` could be used. Variables that avaliable for accessing are: residual table (in quartiles), coefficients, standard error, t-values, and p-values, which are displayed in the output, and variance-covarience matrix  and rank, which are not displayed in the output.
```{r}
# get the information in the output
result = summary_lm2(lm2(formula = Rape ~ Murder+Assault+UrbanPop, data = USArrests, res_display = F), res_display = F)
# something displays in the result
result$resd.tb
# something that does not disply in the result
result$rank
```

### Benchmark `summarylm2` against `summary`:
In this section, we will compare the outputs of `summary_lm2` used in conjunction with `lm2()` to that of `summary()` used in conjunction with `lm()`. To begin, we will save the outputs from both `summary_lm2` and `summary` functions.
```{r}
summary_mod_lm2 = summary_lm2(mod_lm2, res_display = FALSE)
summary_mod_lm = summary(mod_lm)
```

**Compare: Residuals**
```{r}
all.equal(summary_mod_lm2$residuals, summary_mod_lm$residuals) 
bench::mark(summary_mod_lm2$residuals, summary_mod_lm$residuals)
```

**Compare: Coefficients **
```{r}
all.equal(as.matrix(summary_mod_lm2$coefficients), as.matrix(summary_mod_lm$coefficients)) 
bench::mark(as.matrix(summary_mod_lm2$coefficients), as.matrix(summary_mod_lm$coefficients))
```

**Compare: Sigma**
```{r}
all.equal(summary_mod_lm$sigma, summary_mod_lm2$RSE) 
bench::mark(summary_mod_lm$sigma, summary_mod_lm2$RSE) 
```

**Compare: R Squared **
```{r}
all.equal(as.matrix(summary_mod_lm2$r.squared), as.matrix(summary_mod_lm$r.squared)) 
bench::mark(as.matrix(summary_mod_lm2$r.squared), as.matrix(summary_mod_lm$r.squared))
```

**Compare: Adjusted R Squared **
```{r}
all.equal(summary_mod_lm2$adj.r.squared, summary_mod_lm$adj.r.squared)
bench::mark(summary_mod_lm2$adj.r.squared, summary_mod_lm$adj.r.squared)
```

**Compare: F statistics and related p-values**
```{r}
all.equal(summary_mod_lm2$fstatistic, summary_mod_lm$fstatistic)
bench::mark(summary_mod_lm2$fstatistic, summary_mod_lm$fstatistic)
```

**Compare: Unscaled Covariance**
```{r}
all.equal(summary_mod_lm2$cov.unscaled, summary_mod_lm$cov.unscaled)
bench::mark(summary_mod_lm2$cov.unscaled, summary_mod_lm$cov.unscaled)
```